%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,4pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
% No personal projects -- this is a huge red flag that you can't program, add some github links & key points about your projects

% Semi-irrelevant work experience -- lots of people have done highschool jobs, you probably only need one of those three listed, use the rest for demonstrations of your ability to program (e.g., even 207 project is better than office assistant)

% Extra-Curriculars are good, too many words in that section, it should be bullets

% Verb tense is weird, use action words "I restructured and grew the club to more than 20 participating members." is an accomplishment that is easier to digest than a wall of text

% "Arduino's C" is weird, just put "C"
% "LaTeX" is not a programming language
% "Unix command line" is weird, you probably want "Linux administration experience" or something along those lines

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Max Pham} & \textbf{Email} : \href{mailto:max.pham@mail.utoronto.ca}{\underline{max.pham@mail.utoronto.ca}}  \\
   \textbf{Address:} 2605-488 University Ave
 & \textbf{Github:} \href{https://github.com/MaXeraph}{\underline{https://github.com/MaXeraph}}\\
   Toronto, ON M5G 0C1 & \textbf{Portfolio:} \href{https://maxpham.dev/}{\underline{https://maxpham.dev}}\\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
        {University of Toronto}{}
        {Computer Science Specialist | Focus in Computer Systems}{Sep. 2017 -- May. 2022}
      \resumeItemListStart
          \resumeItem{}
            {\textbf{Completed:} Computer Organization, Programming on the Web, Principles of Programming Languages, Engineering Large Software Systems, Algorithm Design, Analysis \& Complexity}
          \resumeItem{}
            {\textbf{In-progress:} Operating Systems Design and Implementation, Database System Technology, Microprocessor Systems, Computer Security, Parallel Programming, Computer Networks, Compilers \& Interpreters}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


% --------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages:}{ Python, C, C++, Java, JavaScript, Racket, HCL}
   }
   \item{\textbf{Technologies:}{ Linux, Terraform, SpringBoot, React, ThymeLeaf, Flask, Express, MongoDB, SQL}}
     
 \resumeSubHeadingListEnd
 
 %-----------EXPERIENCE-----------------
\section{Professional Experiences}
  \resumeSubHeadingListStart

  \resumeSubheading
    {Uken Inc.}{Toronto, ON}
    {Software Engineer}{May 2020 - April 2021}
    \resumeItemListStart
      \resumeItem{}
          {Part of the Services team, which allows for exposure to multiple parts of a backend system as well as games development process. Spun up microservices for the game's shareholders. Using ECS to host the service, configured through Cloudformation and Jenkins for executing jobs.}
     \resumeItem{}
          {Learned and applied new technologies on the go. Participated in designing and implementing Infrastructure-as-Code to manage 400+ repositories and 100+ organization members through code provisioning using Terraform.}
    \resumeItemListEnd
    
    \resumeSubheading
    {Apple Inc.}{Eaton Centre, Toronto}
    {Operations Specialist}{July 2019 - January 2020}
    \resumeItemListStart
      \resumeItem{}
          {Participated in a team effort to ensure inventory accuracy and, in a timely matter, provide the top customer experience, following the APPLE steps of service.}
      \resumeItem{}
          {Frequently achieves 5 points for customer satisfaction and team reviews.}
          
    \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------Projects-----------------
\section{Relevant Projects}
  \resumeSubHeadingListStart

  \resumeSubheading
  {\href{https://github.com/MaXeraph/proj-FakeBirds}{\underline{SDCTools}} [MERN stack]}{}
  {Project Manager, Lead Backend Developer }{January 2020 - April 2020}
  \resumeItemListStart
    \resumeItem{}
        {Delegated proprotional tasks for all teams and members. Organized and maintained the stability of both personnels and the application's production stages. Led the backend team - development of XML-to-JSON parser; API endpoints' design and implementation; Electron-app packaging - with considerations of security and privacy.}
  \resumeItemListEnd

  \resumeSubheading
  {\href{https://github.com/MaXeraph/Portal}{\underline{Portal}} [MERN stack]}{}
  {Backend Developer}{September 2019 - Ongoing}
  \resumeItemListStart
    \resumeItem{}
        {Designed and deployed the app on Heroku. Adhering to RESTful principle for future open-source applications. Data collected from  \href{https://fas.calendar.utoronto.ca/}{\underline{University of Toronto's Calendar}} and with Reddit's related posts, the data is persisted on Atlas@mongoDB. Developed the front-end with React and Tailwind + Backend is supported by Express server.}
    \resumeItem{Current Development: }
        {Adding support for Programs @UofT and other schools. Systematically update database on an annual basis.}
  \resumeItemListEnd

  \resumeSubheading
      {\href{https://lawdesigncolab.ca/redesign-ontario-standard-lease/}{\underline{Ontario Lease Wizard}} [JS + Python]}{}
      {Back-end Developer/Co-lead, Unit Tester, QA}{September 2019 - December 2019}
    \resumeItemListStart
      \resumeItem{}
          {Partner with Design and Co, a non-profit, to produce a more user-friendly and transparent platform for Landlords/Tenants to sign new leases. Participated in communication with Partners, as well as take on facilitator role to make sure the project goes as plan.}
      \resumeItem{}
          {Responsible for the PDF formulation system using Python. Took part in infrastructural backend, serving React with Flask.  Partaking in webpage application from Figma prototype.}
    \resumeItemListEnd



    \resumeSubHeadingListEnd


%-----------Extra-C Activities-----------------
\section{Extra-Curricular Activities}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.instagram.com/autonomousrobotclub/}{\underline{Autonomous Robotics Club}}}{Magee Secondary School, Vancouver, BC}
      {Co-founder, Back-end Developer}{September 2016 - May 2017}
      \resumeItemListStart
        \resumeItem{}
            {Originally non-operational, the club was revived and restructured from the ground up to its updated form with more than 20 recurring members participation. Negotiated and recycled broken computers from teachers to create a fleet of UNIX-based development desktops for members to learn and develop. }
        \resumeItem{}
            {Co-lead in back-end development and vehicle design of a self-driving 3d-printed car and a quadruped spider. Instructed members in basic wiring, soldering, coding (C\#) and safety training for 3d-printer.}
        % \resumeItem{Current State : }
        %     {ARC is now one of the most popular applied science club at school, with its current phase is to train multiple cars to race in obstacle-filled map. With rapid expansion and popularity, the club was sponsored a 3d-Printer given by the generous donation by the school, which was a 10-hour collaboration from every member of the club to build from its bolts.}
      \resumeItemListEnd

    % \resumeSubheading
    %   {Magee e-Sports Club}{Magee Secondary School}
    %   {President}{Sep 2016 - May 2017}
    %   \resumeItemListStart
    %     \resumeItem{}
    %         {Organized weekly SmashBros meetups as well as viewing parties for gaming enthusiasts.}
    %     \resumeItem{}
    %         {Initiated collaborations with Table-top club and the official support from the UBC eSports Association. Helped carried out a spring break tournament for members from high schools in the Vancouver area to participate. Most noticeably, the League of Legends Worlds 2016 Viewing Party had 30 participants, both members and non-members.}
    %     \resumeItemListEnd
    \resumeSubHeadingListEnd

 % -------------------------------------
\end{document}
